---
title: "Lab 00 - Hello IDS!"
author: "Edwin"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Kiet", "Edwin", "Jack", 
           "Ruth", "Sidd", "Minhxi"),
  github_username = c("VKLam", "Edw12", "JackHutcheson", 
                      "RuthAsh", "siddpungi", "Jiang-Mingxi"), 
  colour = c("red", "maroon", "green", 
             "purple", "purple", "darkred"),
  hobby = c("MMA", "cooking", "football", 
            "watching movies", "basketball", "reading"),
  favourite_number = c(4, 5, 4, 2, 7, 6)
  )
team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


*This is a graph that shows the github username, favourite number and favourite colour of the team* 

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Username", 
          y = "Favourite Number",
          title = "Team Graph for Favourite Number")
```

*This is a graph that shows the github username, favourite number and favourite colour of the team*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*A tally could be appropriate, but it depends on the size of the dataset*
